Fast Nearest Neighbour Classification

### 2016-06-22 paper/paper.tex
translate pres

\title{Fast Nearest Neighbour Classification}
\subtitle{\textnormal{\small{Seminar\\
Intelligent Software Systems\\
Summer semester 2015\\\vspace{1\baselineskip}
Lecturer: Stefan Fricke\\\vspace{2\baselineskip}
May 2016\\
Supervisor: Stephan Spiegel\\\vspace{1\baselineskip}}}}

@@

\author{Gordon Lesti\\313249\\Course of studies: Bachelor of Computer Science\\gordon.lesti@campus.tu-berlin.de\\\vspace{5\baselineskip}}

>>>>

\title{Fast Nearest Neighbour Classification}
\subtitle{\textnormal{\small{Seminar\\
Intelligent Software Systems\\
Summer semester 2015\\\vspace{1\baselineskip}
Lecturer: Stefan Fricke\\\vspace{2\baselineskip}
June 2016\\
Supervisor: Stephan Spiegel\\\vspace{1\baselineskip}}}}

@@

\author{Gordon Lesti\\Course of studies: Bachelor of Computer Science\\gordon.lesti@campus.tu-berlin.de\\\vspace{5\baselineskip}}
